---
title: "`r input$Title `"
author: "`r input$Author `"
date: "`r Sys.Date()`"

always_allow_html: yes
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    smart: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>



<style type="text/css">

h1.title {
  font-size: 38px;
  color: #001E7E;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: #001E7E;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
}
</style>

# Demographic characteristics at Baseline

<center>


```{r, echo=FALSE, fig.align='center', warning=FALSE}
# filedata_DS() %>% select(DSDECOD) %>% ds_auto_freq_table()
table_1_2()

table_2_2()

table_3_2()

```



# Sequence-by-period AUC statistics

<center>


```{r, echo=FALSE, fig.align='center', warning=FALSE}
# filedata_DS() %>% select(DSDECOD) %>% ds_auto_freq_table()


#table_4_2() #######################


cat("<style>
caption {
      color: blue;
      font-weight: bold;
      font-size: 1.5em;
    }
</style>")

visites_2 = unique(AUC_by_ID()$VISITNUM)


results <- character()



df_split <- split(AUC_by_ID(), AUC_by_ID()$VISITNUM)



# visites <- levels( df.to_exploit_with_sum())




for (i in 1:length(df_split)) {


  tb <- table1(~. |TRTSEQP, data = df_split[[i]],render.continuous=c("Missing Values" = "NMISS","Mean - SD (CV%)"="Mean - SD (CV%)", .="Median [Min, Max]",
                                                                                           "Geo. mean (Geo. CV%)"="GMEAN (GCV%)", . = "Q1 ; Q3 (IQR)") ,topclass="Rtable1-zebra")

  results <- c(results, "Visit : ", names(df_split)[i], tb)
}

asis_output(results)


```

# Primary Endpoint statistics by product

<center>


```{r, echo=FALSE, fig.align='center', warning=FALSE}


# filedata_DS() %>% select(DSDECOD) %>% ds_auto_freq_table()
table_5_2()




```

# Primary endpoint: sequence-by-period subject profile plots AUC

<center>


```{r, echo=FALSE, fig.align='center', warning=FALSE}


# filedata_DS() %>% select(DSDECOD) %>% ds_auto_freq_table()

ggplot(data = dft(), aes(x = VISITNUM, y = LOG, group = USUBJID )) + geom_line() + aes(colour = USUBJID) + facet_grid(TRTSEQP ~ ., labeller = label_both) + ggtitle(" Primary endpoint: sequence-by-period subject profile plots of total sum of plasma essential Amino Acids (eAA) incremental Area Under the Curve")

```

# Primary endpoint: Ratios Test to Control geometric LSmeans and 90% CI and by sequence individual ratios of Test to Control

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}



ggplot(data = ratios_table_gathered(), aes(x = Ratio, y = ratio_value, ylim(0,4), size=2)) +  
      geom_jitter( width = 0.25, height = 0.05,aes( shape = factor(TRTSEQP)) ) + ggtitle(" Primary endpoint: Ratios Test to Control geometric LSmeans and 90% CI and by sequence individual ratios of Test to Control")   + scale_y_continuous(breaks = round(seq(min(ratios_table_gathered()$ratio_value), max(ratios_table_gathered()$ratio_value), by = 0.5),1))+  geom_hline(yintercept=0.8, linetype="dashed", 
                                                                                                                                                                                                                                        color = "red", size=0.8) +  geom_hline(yintercept=1.25, linetype="dashed", 
                                                                                                                                                                                                                                                                               color = "red", size=0.8) + geom_point(data = CI(), aes(x = Ratio , y = Geometric_Mean ), size= 1, color="red") + geom_segment(data = CI(), aes( x = Ratio,y = Lower_Limit, xend = Ratio, yend = Upper_Limit, group = Ratio, color = "green", size = .4, linetype = "dashed" ))

```


# Primary endpoint: mean and 95% CI study product profiles of total sum of plasma essential Amino Acids (eAA)

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}


ggplot(data = CI_spag(), aes(x = LBTPTNUM, y = mean)) + geom_line(aes(color = factor(TRTSEQP))) + facet_grid(VISITNUM~ TRTSEQP , labeller = label_both)  + geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,
                                                                                                                                                                                                           position=position_dodge(.1)) + ggtitle(" Primary endpoint: mean and 95% CI study product profiles of total sum of plasma essential Amino Acids ")

```


# Primary endpoint: Estimate of the analysis of variance (ANOVA) model

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}

datatable(anova_result(),rownames=FALSE, options = list(dom='t',ordering=F,columnDefs = list(list(className = 'dt-center', targets = 0:2))))

table_6_2()

plot(model(), main = "Conditional Standardized Residuals ")

qqnorm(model(), ~ resid(., type = "p"), abline = c(0, 1), main = "Conditional Standardized Residuals ")

hist(resid(model(), type = "pearson"), main = "Conditional Pearsoned Residuals ", xlab = "Pearsoned Residuals")



```

# Sequence-by-period AUC statistics

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}



table_7_2()


cat("<style>
caption {
      color: blue;
      font-weight: bold;
      font-size: 1.5em;
    }
</style>")

visites_2 = unique(AUC_by_ID_secondary()$VISITNUM)


results <- character()



df_split <- split(AUC_by_ID_secondary(), AUC_by_ID_secondary()$VISITNUM)



# visites <- levels( df.to_exploit_with_sum())




for (i in 1:length(df_split)) {


  tb <- table1(~. |TRTSEQP, data = df_split[[i]],render.continuous=c("Missing Values" = "NMISS","Mean - SD (CV%)"="Mean - SD (CV%)", .="Median [Min, Max]",
                                                                                           "Geo. mean (Geo. CV%)"="GMEAN (GCV%)", . = "Q1 ; Q3 (IQR)") ,topclass="Rtable1-zebra")

  results <- c(results, "Visit : ", names(df_split)[i], tb)
}

asis_output(results)







```

# Secondary Endpoint statistics by product

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}



table_8_2()


```

# Secondary endpoint: sequence-by-period subject profile plots AUC

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}



ggplot(data = dft_secondary(), aes(x = VISITNUM, y = LOG, group = USUBJID )) + geom_line() + aes(colour = factor(USUBJID)) + facet_grid(TRTSEQP ~ ., labeller = label_both) + ggtitle(" Secondary endpoint: sequence-by-period subject profile plots of Leucine Concentration incremental Area Under the Curve")




```

# Secondary endpoint: Ratios Test to Control geometric LSmeans and 90% CI and by sequence individual ratios of Test to Control

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}



ggplot(data = ratios_table_gathered_secondary(), aes(x = Ratio, y = ratio_value, ylim(0,4), size=2)) +  
      geom_jitter( width = 0.25, height = 0.05,aes( shape = factor(TRTSEQP)) ) + ggtitle(" Secondary endpoint Leucine Concentration incremental Area Under the Curve: Ratios Test to Control geometric LSmeans and 90% CI and by sequence individual ratios of Test to Control")   + scale_y_continuous(breaks = round(seq(min(ratios_table_gathered_secondary()$ratio_value), max(ratios_table_gathered_secondary()$ratio_value), by = 0.5),1))+  geom_hline(yintercept=0.8, linetype="dashed", 
                                                                                                                                                                                                                                                            color = "red", size=0.8) +  geom_hline(yintercept=1.25, linetype="dashed", 
                                                                                                                                                                                                                                                                                                   color = "red", size=0.8) + geom_point(data = CI_secondary(), aes(x = Ratio , y = Geometric_Mean ), size= 1, color="red") + geom_segment(data = CI_secondary(), aes( x = Ratio,y = Lower_Limit, xend = Ratio, yend = Upper_Limit, group = Ratio, color = "green", size = .4, linetype = "dashed" ))
    
    




```

# Secondary endpoint: mean and 95% CI study product profiles of Leucine Concentration

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}



ggplot(data = CI_spag_secondary(), aes(x = LBTPTNUM, y = mean)) + geom_line(aes(color = factor(TRTSEQP))) + facet_grid(VISITNUM~ TRTSEQP , labeller = label_both)  + geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,
                                                                                                                                                                                                                         position=position_dodge(.1)) + ggtitle(" Secondary endpoint: mean and 95% CI study product profiles of Leucine Concentration incremental Area Under the Curve")




```

# Secondary endpoint: Estimate of the analysis of variance (ANOVA) model

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}

datatable(anova_result_secondary(),rownames=FALSE, options = list(dom='t',ordering=F,columnDefs = list(list(className = 'dt-center', targets = 0:2))))



plot(model_secondary(), main = "Conditional Standardized Residuals ")

qqnorm(model_secondary(), ~ resid(., type = "p"), abline = c(0, 1), main = "Conditional Standardized Residuals ")

hist(resid(model_secondary(), type = "pearson"), main = "Conditional Pearsoned Residuals ", xlab = "Pearsoned Residuals")



```

# Sequence-by-period Tmax statistics

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}

table_10_2()


cat("<style>
caption {
      color: blue;
      font-weight: bold;
      font-size: 1.5em;
    }
</style>")

visites_2 = unique(df_anotated_third()$VISITNUM)


results <- character()



df_split <- split(df_anotated_third(), df_anotated_third()$VISITNUM)



# visites <- levels( df.to_exploit_with_sum())




for (i in 1:length(df_split)) {


  tb <- table1(~. |TRTSEQP, data = df_split[[i]],render.continuous=c("Missing Values" = "NMISS","Mean - SD (CV%)"="Mean - SD (CV%)", .="Median [Min, Max]",
                                                                                           "Geo. mean (Geo. CV%)"="GMEAN (GCV%)", . = "Q1 ; Q3 (IQR)") ,topclass="Rtable1-zebra")

  results <- c(results, "Visit : ", names(df_split)[i], tb)
}

asis_output(results)







```

# Secondary Endpoint Tmax statistics by product

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}

table_11_2()


```

# Secondary Endpoint Cmax statistics by product

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}

table_12_2()



```

# Secondary Endpoint by product and timepoint statistics

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}


table_13_2()

cat("<style>
caption {
      color: blue;
      font-weight: bold;
      font-size: 1.5em;
    }
</style>")

visites_2 = unique(detailed_concentrations_by_timepoint_and_subject_secondary()$VISITNUM)


results <- character()



df_split <- split(detailed_concentrations_by_timepoint_and_subject_secondary(), detailed_concentrations_by_timepoint_and_subject_secondary()$LBTPTNUM)



# visites <- levels( df.to_exploit_with_sum())




for (i in 1:length(df_split)) {


  tb <- table1(~SUM |produit, data = df_split[[i]],render.continuous=c("Missing Values" = "NMISS","Mean - SD (CV%)"="Mean - SD (CV%)", .="Median [Min, Max]",
                                                                                           "Geo. mean (Geo. CV%)"="GMEAN (GCV%)", . = "Q1 ; Q3 (IQR)") ,topclass="Rtable1-zebra")

  results <- c(results, "Timepoint : ", names(df_split)[i], tb)
}

asis_output(results)





```

# Secondary endpoint: sequence-by-period subject profile plots Cmax

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}


ggplot(data = dft_third(), aes(x = VISITNUM, y = LOG, group = USUBJID )) + geom_line() + aes(colour = factor(USUBJID)) + facet_grid(TRTSEQP ~ ., labeller = label_both) + ggtitle(" Secondary endpoint: sequence-by-period subject profile plots of  Cmax observed (?mol/L) over 4 hours")


```

# Secondary endpoint Cmax: Ratios Test to Control geometric LSmeans and 90% CI and by sequence individual ratios of Test to Control

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}


ggplot(data = ratios_table_gathered_third_Cmax(), aes(x = Ratio, y = ratio_value, ylim(0,4), size=2)) +  
      geom_jitter( width = 0.25, height = 0.05,aes( shape = factor(TRTSEQP)) ) + ggtitle("Secondary endpoint Cmax observed: Ratios Test to Control geometric LSmeans, 90% CI & by sequence individual ratios of Test to Control")  + scale_y_continuous(breaks = round(seq(min(ratios_table_gathered_third_Cmax()$ratio_value), max(ratios_table_gathered_third_Cmax()$ratio_value), by = 0.5),1))+  geom_hline(yintercept=0.8, linetype="dashed", 
                                                                                                                                                                                                                                                              color = "red", size=0.8) +  geom_hline(yintercept=1.25, linetype="dashed", 
                                                                                                                                                                                                                                                                                                     color = "red", size=0.8) + geom_point(data = CI_third_Cmax(), aes(x = Ratio , y = Geometric_Mean ), size= 1, color="red") + geom_segment(data = CI_third_Cmax(), aes( x = Ratio,y = Lower_Limit, xend = Ratio, yend = Upper_Limit, group = Ratio, color = "green", size = .4, linetype = "dashed" ))

```


# Secondary endpoint: Estimate of the analysis of variance (ANOVA) model - Cmax



<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}

datatable(anova_result_third_Cmax(),rownames=FALSE, options = list(dom='t',ordering=F,columnDefs = list(list(className = 'dt-center', targets = 0:2))))



plot(model_third_Cmax(), main = "Conditional Standardized Residuals ")

qqnorm(model_third_Cmax(), ~ resid(., type = "p"), abline = c(0, 1), main = "Conditional Standardized Residuals ")

hist(resid(model_third_Cmax(), type = "pearson"), main = "Conditional Pearsoned Residuals ", xlab = "Pearsoned Residuals")



```


# Secondary endpoint: Estimate of the analysis of variance (ANOVA) model - Tmax

<center>

```{r, echo=FALSE, fig.align='center', warning=FALSE}

datatable(anova_result_third_Tmax(),rownames=FALSE, options = list(dom='t',ordering=F,columnDefs = list(list(className = 'dt-center', targets = 0:2))))



plot(model_third_Tmax(), main = "Conditional Standardized Residuals ")

qqnorm(model_third_Tmax(), ~ resid(., type = "p"), abline = c(0, 1), main = "Conditional Standardized Residuals ")

hist(resid(model_third_Tmax(), type = "pearson"), main = "Conditional Pearsoned Residuals ", xlab = "Pearsoned Residuals")



```