---
title: "`r input$Title `"
author: "`r input$Author `"
date: "`r Sys.Date()`"

always_allow_html: yes
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    smart: false

---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>


<style type="text/css">

h1.title {
  font-size: 38px;
  color: #001E7E;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: #001E7E;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
}
</style>



```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Subjects Disposition 

<center>


```{r, echo=FALSE, fig.align='center', warning=FALSE}
# filedata_DS() %>% select(DSDECOD) %>% ds_auto_freq_table()
table_1()

```



```{r, echo=FALSE, fig.align='center', warning=FALSE, results='asis'}
# filedata_DS() %>% select(DSDECOD) %>% ds_auto_freq_table()
knit_print(table_0())

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>



# Descriptive Statistics of demographic data

<center>


```{r pressure, echo=FALSE, fig.align='center', warning=FALSE}
# demographic_characteristics() %>% ds_summary_stats()

table_2()
```

<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>


# Duration Descriptive Statistics

<center>


```{r, echo=FALSE, fig.align='center', warning=FALSE}

# durations()%>% ds_summary_stats()

table_3()

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>


# Age Statistics

<center>


```{r, echo=FALSE, warning=FALSE}

# age() %>% ds_summary_stats()

table_4()

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>



# Area Under Curve Statistics by technic

<center>


```{r, echo=FALSE, warning=FALSE}
# df.AUC() %>% group_by(as.factor(visit)) %>% select(iAUCS) %>% ds_summary_stats()

# options(width = 2000)

# df.AUC() %>% ds_auto_group_summary()

table_5()

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>





# Distribution of iAUC values by visit

<center>



```{r, echo=FALSE, warning=FALSE}

ggplot(data = df.AUC(), aes(y = iAUCS, fill = as.factor(VISITNUM))) + geom_boxplot()

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>


# iAUC Outliers

<center>



```{r, echo = FALSE, warning=FALSE}

library(DT)
datatable(df.Outliers(),rownames=FALSE, options = list(dom='t',ordering=F,columnDefs = list(list(className = 'dt-center', targets = 0:2)))


)

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>


# Histogram by visit

<center>



```{r, echo=FALSE, warning=FALSE}

ggplot(data = df.AUC(), aes(x = iAUCS)) + geom_histogram( binwidth = 25000,colour = "black", fill = "white")  + geom_density(aes(y=25000 * ..count..),color="darkblue", fill="lightblue", alpha = 0.2)  + facet_grid(VISITNUM ~ ., labeller = label_both)

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Title 

<center>



```{r, echo=FALSE, warning=FALSE}


ggplot(data = df.AUC(), aes(x = VISITNUM, y = iAUCS, group = USUBJID)) + geom_line() + aes(colour = factor(USUBJID))

```

<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Overall 

<center>




```{r, echo = FALSE, error=FALSE, warning=FALSE}

# summarytools::freq(df.AUC()$visit)

table_6()

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Overall bar plot of percentage of non missing observations - Bar plot by visit

<center>



```{r,echo=FALSE, warning=FALSE}

ggplot(data=df.missing_data(), aes(x=as.factor(VISITNUM))) + geom_bar(aes(y = (..count..)/sum(..count..)), group = 1) + ggtitle("Percentage of non missing iAUCs per visit")

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Total sum of the amount of the eAA (pmol) at each timepoint - Summary

<center>



```{r, echo=FALSE, results = "asis" , warning=FALSE }
library(table1)
library(knitr)
knit_print(table_7())

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>



# Total sum of the amount of the biomarker at each point

<center>



```{r,echo = FALSE, results='asis', warning=FALSE}

cat("<style>
caption {
      color: blue;
      font-weight: bold;
      font-size: 1.5em;
    }
</style>")

results <- character()



df_split <- split(df.to_exploit_with_sum(), df.to_exploit_with_sum()$VISITNUM)



visites <- levels( df.to_exploit_with_sum())




for (i in 1:length(df_split)) {


  tb <- table1(~EAASUM, data = df_split[[i]],render.continuous=c("Missing Values" = "NMISS","Mean - SD (CV%)"="Mean - SD (CV%)", .="Median [Min, Max]",
                                                                                           "Geo. mean (Geo. CV%)"="GMEAN (GCV%)", . = "Q1 ; Q3 (IQR)") ,topclass="Rtable1-zebra")

  results <- c(results, "Visit : ", names(df_split)[i], tb)
}

asis_output(results)



 
 


```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

<center>


```{r, echo = FALSE, out.width = '100%', warning=FALSE}

ggplot(data = df.to_exploit_with_sum(), aes(y = EAASUM, group = VISITNUM)) + geom_boxplot() + facet_wrap(LBTPTNUM ~ ., labeller = label_both, scales = "free")

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

<center>


```{r, echo = FALSE, out.width = '100%', warning=FALSE}

ggplot(data = df.to_exploit_with_sum(), aes(x = EAASUM)) + geom_histogram( binwidth = 250,colour = "black", fill = "white")  + geom_density(aes(y=250 * ..count..),color="darkblue", fill="lightblue", alpha = 0.2)  + facet_grid(VISITNUM ~ LBTPTNUM, labeller = label_both, scales = "free") + theme(axis.text.x = element_text(angle = 90, hjust = 1), strip.text.x = element_text(
        size = 5))

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Total sum of the amount of the eAA (pmol) at each timepoint  - Listing of outliers

<center>



```{r, echo = FALSE, warning=FALSE}


datatable(df.full_outliers(),rownames=FALSE, options = list(dom='t',ordering=F,columnDefs = list(list(className = 'dt-center', targets = 0:2)))


)
```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint: Summary

<center>



```{r, echo = FALSE, warning=FALSE}


table_8()

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>



# Secondary endpoint: Boxplot by visit

<center>



```{r, echo = FALSE, warning=FALSE}


ggplot(data = df.AUC_secondary(), aes(y = iAUCS, fill = as.factor(VISITNUM))) + geom_boxplot()+ scale_fill_brewer(palette = "Dark2")

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint: Listing of outliers

<center>



```{r, echo = FALSE, warning=FALSE}

datatable(df.Outliers_secondary(),rownames=FALSE, options = list(dom='t',ordering=F,columnDefs = list(list(className = 'dt-center', targets = 0:2))))



```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint: Histogram by visit

<center>



```{r, echo = FALSE, warning=FALSE}

ggplot(data = df.AUC_secondary(), aes(x = iAUCS)) + geom_histogram( binwidth = 25000,colour = "black", fill = "white")  + geom_density(aes(y=25000 * ..count..),color="darkblue", fill="lightblue", alpha = 0.2)  + facet_grid(VISITNUM ~ ., labeller = label_both)


```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

#  Secondary endpoint: Spaghetti plot by visit

<center>



```{r, echo = FALSE, warning=FALSE}


ggplot(data = df.AUC_secondary(), aes(x = VISITNUM, y = iAUCS, group = USUBJID)) + geom_line() + aes(colour = factor(USUBJID))

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint : C  Max observed over the experiment period - Summary

<center>



```{r, echo = FALSE, warning=FALSE}


table_9()

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint : C  Max observed over the experiment period - Boxplot by visit

<center>



```{r, echo = FALSE, warning=FALSE}


ggplot(data = df.third_endpoint(), aes(y = Cmax, fill = as.factor(VISITNUM))) + geom_boxplot()+ scale_fill_brewer(palette = "Dark2")

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint : C  Max observed over the experiment period - Listing of outliers

<center>



```{r, echo = FALSE, warning=FALSE}

datatable(df.Cmax_outliers(),rownames=FALSE, options = list(dom='t',ordering=F,columnDefs = list(list(className = 'dt-center', targets = 0:2))))





```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint : C  Max observed over the experiment period - Spaghetti plot by visit

<center>



```{r, echo = FALSE, warning=FALSE}

ggplot(data = df.third_endpoint(), aes(x = VISITNUM, y = Cmax, group = USUBJID)) + geom_line() + aes(colour = factor(USUBJID))


```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint : T  Max observed over the experiment period - Spaghetti plot by visit

<center>



```{r, echo = FALSE, warning=FALSE}

table_10()

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint : T  Max observed over the experiment period - Boxplot plot by visit

<center>



```{r, echo = FALSE, warning=FALSE}

ggplot(data = df.third_endpoint(), aes(y = Tmax, fill = as.factor(VISITNUM))) + geom_boxplot()+ scale_fill_brewer(palette = "Dark2")

```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>

# Secondary endpoint : T  Max observed over the experiment period - List of outliers

<center>



```{r, echo = FALSE, warning=FALSE}

datatable(df.Tmax_outliers(),rownames=FALSE, options = list(dom='t',ordering=F,columnDefs = list(list(className = 'dt-center', targets = 0:2))))


```
<p style="page-break-after: always;">&nbsp;</p>
<p style="page-break-before: always;">&nbsp;</p>


# Secondary endpoint : T  Max observed over the experiment period - Spaghetti plot by visit 

<center>



```{r, echo = FALSE, warning=FALSE}

ggplot(data = df.third_endpoint(), aes(x = VISITNUM, y = Tmax, group = USUBJID)) + geom_line() + aes(colour = factor(USUBJID))

```



